SIMD-vectorized Chemical Source Term Evaluation

### 2017-02-21 paper.tex
hyphens, cpu defn

Single Instruction, Multiple-Data (SIMD) processing, also known as vector-processing, is an important parallel computing paradigm used increasingly in scientific computing.
Traditional multi-core parallelism is often used to increase CPU performance, however SIMD processors---and the related Single Instruction, Multiple Thread (SIMT) processors, e.g. graphics processing units (GPUs)---have gained recognition due to their increased floating operation throughput.
The parallel programming standard OpenCL~\cite{stone2010opencl} has further enabled adoption of vector-processing based codes in scientific computing by providing a common application program interface (API) for execution on heterogeneous systems (e.g. CPU, GPU, etc.).

>>>>

Single-Instruction, Multiple-Data (SIMD) processing, also known as vector-processing, is an important parallel computing paradigm used increasingly in scientific computing.
Traditional multi-core parallelism is often used to increase central processing unit (CPU) performance, however SIMD processors---and the related Single-Instruction, Multiple-Thread (SIMT) processors, e.g. graphics processing units (GPUs)---have gained recognition due to their increased floating operation throughput.
The parallel programming standard OpenCL~\cite{stone2010opencl} has further enabled adoption of vector-processing based codes in scientific computing by providing a common application program interface (API) for execution on heterogeneous systems (e.g. CPU, GPU, etc.).
